Errata

### 2025-04-06 tex/Methodology.tex
Fix typos and update references in Methodology section of the manuscript. Corrected "Köhn1929" to "Kohn1929" and updated citation for the $bestNormalize$ package from Peterson2021 to Peterson2020.

Before commencing experimental manipulations, a suite of baseline soil properties was determined on the sieved ($<$\SI{2}{\milli\metre}), air-dried field samples. Physical properties measured included bulk density (BD), determined gravimetrically, and particle size distribution (PSD). PSD was analyzed following the method of \citet{Köhn1929}, which combines sieving for fractions larger than \SI{20}{\micro\metre} with pipetting for fractions smaller than \SI{20}{\micro\metre} (Manuscript 1). Soil texture classes were subsequently interpreted based on World Reference Base (WRB) guidelines \citep{Jahn2006}. Chemical properties assessed included soil pH and electrical conductivity (EC), measured in soil:water suspensions (1:2.5 or 1:5 ratios) using calibrated meters (Manuscripts 1, 3 and 5). Total carbon (C\textsubscript{T}) and total nitrogen (N\textsubscript{T}) contents were quantified via oxidative heat combustion at high temperatures (\SI{1150}{\degreeCelsius}) using an elemental analyzer (Vario EL III, Euro EA) (Manuscripts 1, 3, 4 and 5). Soil organic carbon (SOC) was typically calculated by subtracting the inorganic carbon (SIC) content from the C\textsubscript{T} content. SIC was measured using a calcimeter (Scheibler method) or determined through acid digestion, particularly for soils with pH values exceeding 6.7--7.0 (Manuscripts 1, 3 and 4). Additionally, concentrations of various inorganic ions (Cl$^{-}$, NO$_{3}^{-}$, PO$_{4}^{3-}$, SO$_{4}^{2-}$, Na$^{+}$, Ca$^{2+}$) were measured in soil leachates prepared from the samples, utilizing ion chromatography (IC) (Manuscript 3).

@@

Analysis of variance (ANOVA) and analysis of covariance (ANCOVA) were also employed, particularly to assess differences in measured properties between treatments and across sites or horizons. Where applicable, soil baseline variables were used as covariates in ANCOVA (Manuscripts 2 and 5). Non-parametric tests, such as the Kruskal-Wallis test followed by Mann-Whitney post-hoc tests, were used when normality or homoscedasticity assumptions were violated (Manuscript 3). Data transformations were applied when necessary, using the $bestNormalize$ package \citep{Peterson2019,Peterson2021}. The Dunn-Šidák correction was implemented for multiple comparisons \citep{Hothorn2008}.

>>>>

Before commencing experimental manipulations, a suite of baseline soil properties was determined on the sieved ($<$\SI{2}{\milli\metre}), air-dried field samples. Physical properties measured included bulk density (BD), determined gravimetrically, and particle size distribution (PSD). PSD was analyzed following the method of \citet{Kohn1929}, which combines sieving for fractions larger than \SI{20}{\micro\metre} with pipetting for fractions smaller than \SI{20}{\micro\metre} (Manuscript 1). Soil texture classes were subsequently interpreted based on World Reference Base (WRB) guidelines \citep{Jahn2006}. Chemical properties assessed included soil pH and electrical conductivity (EC), measured in soil:water suspensions (1:2.5 or 1:5 ratios) using calibrated meters (Manuscripts 1, 3 and 5). Total carbon (C\textsubscript{T}) and total nitrogen (N\textsubscript{T}) contents were quantified via oxidative heat combustion at high temperatures (\SI{1150}{\degreeCelsius}) using an elemental analyzer (Vario EL III, Euro EA) (Manuscripts 1, 3, 4 and 5). Soil organic carbon (SOC) was typically calculated by subtracting the inorganic carbon (SIC) content from the C\textsubscript{T} content. SIC was measured using a calcimeter (Scheibler method) or determined through acid digestion, particularly for soils with pH values exceeding 6.7--7.0 (Manuscripts 1, 3 and 4). Additionally, concentrations of various inorganic ions (Cl$^{-}$, NO$_{3}^{-}$, PO$_{4}^{3-}$, SO$_{4}^{2-}$, Na$^{+}$, Ca$^{2+}$) were measured in soil leachates prepared from the samples, utilizing ion chromatography (IC) (Manuscript 3).

@@

Analysis of variance (ANOVA) and analysis of covariance (ANCOVA) were also employed, particularly to assess differences in measured properties between treatments and across sites or horizons. Where applicable, soil baseline variables were used as covariates in ANCOVA (Manuscripts 2 and 5). Non-parametric tests, such as the Kruskal-Wallis test followed by Mann-Whitney post-hoc tests, were used when normality or homoscedasticity assumptions were violated (Manuscript 3). Data transformations were applied when necessary, using the $bestNormalize$ package \citep{Peterson2019,Peterson2020}. The Dunn-Šidák correction was implemented for multiple comparisons \citep{Hothorn2008}.
